### 2012-02-07 final/cap-ameacas.tex
mais um tapa no cap de planejamento
super esqueletao -- agora vai

@@

>>>>

SEPARAR AQUI EM INTERNAL, EXTERNAL E CONSTRUCT VALIDITY

TDD is very popular among agilists. The brazilian agile community is still young and one can empirically perceive that many developers are really influenced by literature, and not by their own experience or knowledge on the subject. Therefore, the desirability bias may affect this research, as the participant could have said not that he thinks, but what he has read. In order to reduce this problem, the research tried to eliminate answers that were not well explained.
Although almost all participants affirmed that the exer- cises contain real class design issues, they are still small in comparison to real software. The simplicity may have affected the code generated by the participants.
Some participants did not finish the exercises. This may affect the code metrics. That is why specialists were invited to evaluated the code. They were warned about this problem, and they evaluated not only the final generated code, but the final design the participant has intended (which can be easily seen by just looking the code).

* * * * * *

@@

opiniao do pesquisador para selecionar os candidatos para entrevista

### 2012-02-07 final/cap-tdd.tex
super esqueletao -- agora vai

Como mencionado acima, os praticantes de TDD acreditam que os testes de unidade
podem ajudá-los a criar um design de classes de qualidade. Uma das explicações mais
populares para esse fenômeno é a relação
entre um código que possui uma alta testabilidade, ou seja, é fácil de ser testado
por meio de um teste de unidade, e um design de classes de alta qualidade.
Segundo Michael Feathers \cite{feathers-synergy}, 
por causa dessa sinergia muito
grande entre uma classe com alta testabilidade e um bom \textit{design de classes}: se o
programador busca por testabilidade, acaba criando um bom \textit{design de classes}; se 
busca por um bom \textit{design de classes}, acaba escrevendo classes mais
testáveis.

>>>>

Como mencionado acima, os praticantes de TDD acreditam que os testes de unidade
podem ajudá-los a criar um design de classes de qualidade. Uma das explicações mais
populares para esse fenômeno é a relação
entre um código que possui uma alta testabilidade, ou seja, é fácil de ser testado
por meio de um teste de unidade, e um design de classes de alta qualidade.
Segundo Feathers \cite{feathers-synergy}, 
por causa dessa sinergia muito
grande entre uma classe com alta testabilidade e um bom \textit{design de classes}: se o
programador busca por testabilidade, acaba criando um bom \textit{design de classes}; se 
busca por um bom \textit{design de classes}, acaba escrevendo classes mais
testáveis.
